---
title: "Bayes Continued"
author: "Anna Yaggi"
date: '2022-11-30'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
Sys.setenv(MAKEFLAGS = "-j4") # four cores used
library(dplyr)
library(rvest)
library(rstan)
library(gdata)
library(bayesplot)
library(ggplot2)
```

```{r}
setwd("~/DEI Tech Analysis/deiSurveyShiny/Anna's Code")
anna_course_df <- course_df
attach(anna_course_df)
#View(anna_course_df)
```

***detect CAS***
```{r}
#creating a variable to detect whether a course is in CAS or not#
detect_CAS <- str_detect(course, "CAS")
detect_CAS <- ifelse(detect_CAS == TRUE, 1, 0)
detect_CAS <- as.vector(detect_CAS)
anna_course_df <- cbind(anna_course_df, detect_CAS)
#View(anna_course_df)
```

***detect ENG***
```{r}
#creating a variable to detect whether a course is in ENG or not#
detect_ENG <- str_detect(course, "ENG")
detect_ENG <- ifelse(detect_ENG == TRUE, 1, 0)
detect_ENG <- as.vector(detect_ENG)
anna_course_df <- cbind(anna_course_df, detect_ENG)
#View(anna_course_df)
```

***detect CS***
```{r}
#creating a variable to detect whether a course is in CS or not#
detect_CS <- str_detect(course, "CS")
detect_CS <- ifelse(detect_CS == TRUE, 1, 0)
detect_CS <- as.vector(detect_CS)
anna_course_df <- cbind(anna_course_df, detect_CS)
#View(anna_course_df)
```

***detect DS***
```{r}
#creating a variable to detect whether a course is in DS or not#
detect_DS <- str_detect(course, "DS")
detect_DS <- ifelse(detect_DS == TRUE, 1, 0)
detect_DS <- as.vector(detect_DS)
anna_course_df <- cbind(anna_course_df, detect_DS)
#View(anna_course_df)
```

***detect MA***
```{r}
#creating a variable to detect whether a course is in MA or not#
detect_MA <- str_detect(course, "MA")
detect_MA <- ifelse(detect_MA == TRUE, 1, 0)
detect_MA <- as.vector(detect_MA)
anna_course_df <- cbind(anna_course_df, detect_MA)
#View(anna_course_df)
```


***detect EK***
```{r}
#creating a variable to detect whether a course is in EK or not#
detect_EK <- str_detect(course, "EK")
detect_EK <- ifelse(detect_EK == TRUE, 1, 0)
detect_EK <- as.vector(detect_EK)
anna_course_df <- cbind(anna_course_df, detect_EK)
#View(anna_course_df)
```

***detect IS***
```{r}
#creating a variable to detect whether a course is in EK or not#
detect_IS <- str_detect(course, "IS")
detect_IS <- ifelse(detect_IS == TRUE, 1, 0)
detect_IS <- as.vector(detect_IS)
anna_course_df <- cbind(anna_course_df, detect_IS)
#View(anna_course_df)
```

#note: there were very few PY, CH, and EC courses, so i chose to use these all combined as a reference variable

***creating a variable to extract the class LEVEL***
```{r}
extract_level <- str_extract(course, "\\d+")
extract_level <- strtoi(extract_level)
extract_level <- extract_level/100
extract_level <- floor(extract_level)
#anna_course_df <- cbind(anna_course_df, extract_level)
#View(anna_course_df)
```


***creating a variable to detect the class level 100***
```{r}
detect_level1 <- str_detect(extract_level, "1")
detect_level1 <- ifelse(detect_level1 == TRUE, 1, 0)
anna_course_df <- cbind(anna_course_df, detect_level1)
#View(anna_course_df)
```

***creating a variable to detect the class level 200***
```{r}
detect_level2 <- str_detect(extract_level, "2")
detect_level2 <- ifelse(detect_level2 == TRUE, 1, 0)
anna_course_df <- cbind(anna_course_df, detect_level2)
#View(anna_course_df)
```

***creating a variable to detect the class level 300***
```{r}
detect_level3 <- str_detect(extract_level, "3")
detect_level3 <- ifelse(detect_level3 == TRUE, 1, 0)
anna_course_df <- cbind(anna_course_df, detect_level3)
#View(anna_course_df)
```

***creating a variable to detect the class level 400***
```{r}
detect_level4 <- str_detect(extract_level, "4")
detect_level4 <- ifelse(detect_level4 == TRUE, 1, 0)
anna_course_df <- cbind(anna_course_df, detect_level4)
View(anna_course_df)
```

***Department Dummy Matrix***
```{r}
dep_dummy <- cbind(detect_CS, detect_DS, detect_EK, detect_IS, detect_MA)
View(dep_dummy)
```

Level Dummy Matrix
```{r}
lev_dummy <- cbind(detect_level1, detect_level2, detect_level3, detect_level4)
View(lev_dummy)
```


***Creating a variable to create levels of satisfaction***
```{r}
#a little stuck here
```




#creating the stan data 
#for X = course and Y = satsifaction level
##question: here X is course, but shouldn't it be demographic information?
```{r}
X_dep <- dep_dummy
X_lev <- lev_dummy
y <- anna_course_df$response
#number of courses
N <- 64
#number of columns
K <- 9
D_dep <- dim(X_dep)[2]
D_lev <- dim(X_lev)[2]

Model4_grouping_data <- list(N = N, K=K, D_dep=D_dep, D_lev = D_lev, X_dep = X_dep, X_lev = X_lev, y = y)

```

#running model 4 grouping
```{r}
stanc("Model4_grouping.stan")
Model4_grouping <- "Model4_grouping.stan"
fit <- stan(file = Model4_grouping, data = Model4_grouping_data, warmup = 50, iter = 100, chains = 4, cores = 4, thin = 1)
```





