---
title: "Beginning Bayes / Multilevel Regression"
author: "Anna Yaggi"
date: '2022-10-19'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


Installing packages
```{r}
library(tidyverse)
Sys.setenv(MAKEFLAGS = "-j4") # four cores used
#install.packages(c("Rcpp", "RcppEigen", "RcppParallel", "StanHeaders"), type = "source")
#install.packages("rstan", type = "source")
library(dplyr)
library(rvest)
library(rstan)
library(gdata)
library(bayesplot)

```

clean data, create a data set with major as a dummy variable, and 
```{r}
setwd("~/DEI Tech Analysis/deiSurveyShiny/Anna's Code")

#satisfaction with CS111 dummy matrix
#Q11_1_dummy <- model.matrix(~Q11_1, data = ddf)
qdf <- ddf %>% filter(!is.na(Q11_1), Q11_1 != "Did not take this course.")

#satisfaction with CS11 ordered
Q11_1_ordered_vec <- factor(qdf$Q11_1, levels = satisfaction_level)


#major dummy matrix
Qmajor_dummy <- model.matrix(~major, data = qdf)

#international student dummy matrix
qdf$international[is.na(qdf$international)] <- 0
Qinternational_dummy <- model.matrix(~international, data = qdf)

#gender dummy matrix
qdf$gender[is.na(qdf$gender)] <- 0
Qgender_dummy <- model.matrix(~gender, data = qdf)

#race dummy matrix
qdf$race[is.na(qdf$race)] <- 0
Qrace_dummy <- model.matrix(~race, data = qdf)

#binding all of the dummy matrices
first_dummy <- cbind(Qmajor_dummy, Qinternational_dummy, Qgender_dummy, Qrace_dummy)


```




#creating the stan data (simple data set)
```{r}
X <- Qmajor_dummy
y <- Q11_1_ordered_vec
N <- length(y)
K <- 5
D <- dim(X)[2]

stan_data <- list(N = N, K=K, D=D, X = X, y = y)
#lm1 <- lm(y ~ X)
#summary(lm1)
```


```{r}
stanc("stan_model1.stan")
stan_model1 <- "Stan_model1.stan"
fit <- stan(file = stan_model1, data = stan_data, warmup = 500, iter = 1000, chains = 4, cores = 4, thin = 1)
fit
```

OK, I understand what the problem is with the above model. The matrices are not the same size  <- they are the same length (640), but have a different amount of columns. I don't know what to do. The Stan user guide says the same thing. Not sure what to do. 
We may have to go with a different argument to distribution. There is a decent amount of information on it in the user guide, I just have to get to the bottom of it









Note: 
I tried to use race_df to define the race variables but its not working
#using race_df to assign race variables and then creating a dummy variable out of these
 race_df <- ddf %>%
    count(race) %>%
    filter(!str_detect(race, ",")) %>% # assumes each race was picked alone at least once
    transmute(
      name = tolower(race) %>%
        str_extract("[\\w\\s]+") %>%
        str_remove_all("\\s*$") %>%
        str_replace_all("\\s", "_") %>%
        str_c("race_", .),
      race_str = race
    )
  assign("race_df", race_df, envir = topenv())

  race_choice_list <- as.list(race_df$name)
  names(race_choice_list) <- race_df$race_str

  assign("race_choice_list", race_choice_list, envir = topenv())
  race_str_list <- as.list(race_df$race_str)
  names(race_str_list) <- race_df$name
  assign("race_str_list", race_str_list, envir = topenv())





Notes:how to get it from categorical to numerical
  use factors for to specify the levels (for response variables), use course_df
  mutate (as integer)
  look in report folder --> index file, has how to create the variables
  
  
  
  
