# Department Satisfaction


## CAS CH Department Satisfaction

This is taking all the satisfaction responses for each course in the CAS CH and combining them.

```{r CASCH_input}
input <- list(selected_dep = "CAS CH")
dep_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_dep))
```


### Overall Satisfaction

```{r CASCH_plot_overall}
dep_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASCH_plot_gender}
dep_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_dep)
```



### Satisfaction by Race

```{r CASCH_plot_race}
dep_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_dep)
```




## CAS CS Department Satisfaction

This is taking all the satisfaction responses for each course in the CAS CS and combining them.

```{r CASCS_input}
input <- list(selected_dep = "CAS CS")
dep_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_dep))
```


### Overall Satisfaction

```{r CASCS_plot_overall}
dep_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASCS_plot_gender}
dep_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_dep)
```



### Satisfaction by Race

```{r CASCS_plot_race}
dep_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_dep)
```




## CAS MA Department Satisfaction

This is taking all the satisfaction responses for each course in the CAS MA and combining them.

```{r CASMA_input}
input <- list(selected_dep = "CAS MA")
dep_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_dep))
```


### Overall Satisfaction

```{r CASMA_plot_overall}
dep_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASMA_plot_gender}
dep_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_dep)
```



### Satisfaction by Race

```{r CASMA_plot_race}
dep_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_dep)
```




## CAS PY Department Satisfaction

This is taking all the satisfaction responses for each course in the CAS PY and combining them.

```{r CASPY_input}
input <- list(selected_dep = "CAS PY")
dep_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_dep))
```


### Overall Satisfaction

```{r CASPY_plot_overall}
dep_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASPY_plot_gender}
dep_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_dep)
```



### Satisfaction by Race

```{r CASPY_plot_race}
dep_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_dep)
```




## CDS DS Department Satisfaction

This is taking all the satisfaction responses for each course in the CDS DS and combining them.

```{r CDSDS_input}
input <- list(selected_dep = "CDS DS")
dep_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_dep))
```


### Overall Satisfaction

```{r CDSDS_plot_overall}
dep_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CDSDS_plot_gender}
dep_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_dep)
```



### Satisfaction by Race

```{r CDSDS_plot_race}
dep_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_dep)
```




## ENG EC Department Satisfaction

This is taking all the satisfaction responses for each course in the ENG EC and combining them.

```{r ENGEC_input}
input <- list(selected_dep = "ENG EC")
dep_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_dep))
```


### Overall Satisfaction

```{r ENGEC_plot_overall}
dep_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r ENGEC_plot_gender}
dep_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_dep)
```



### Satisfaction by Race

```{r ENGEC_plot_race}
dep_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_dep)
```




## ENG EK Department Satisfaction

This is taking all the satisfaction responses for each course in the ENG EK and combining them.

```{r ENGEK_input}
input <- list(selected_dep = "ENG EK")
dep_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_dep))
```


### Overall Satisfaction

```{r ENGEK_plot_overall}
dep_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r ENGEK_plot_gender}
dep_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_dep)
```



### Satisfaction by Race

```{r ENGEK_plot_race}
dep_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_dep)
```




## QST BA Department Satisfaction

This is taking all the satisfaction responses for each course in the QST BA and combining them.

```{r QSTBA_input}
input <- list(selected_dep = "QST BA")
dep_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_dep))
```


### Overall Satisfaction

```{r QSTBA_plot_overall}
dep_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r QSTBA_plot_gender}
dep_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_dep)
```



### Satisfaction by Race

```{r QSTBA_plot_race}
dep_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_dep)
```




## QST IS Department Satisfaction

This is taking all the satisfaction responses for each course in the QST IS and combining them.

```{r QSTIS_input}
input <- list(selected_dep = "QST IS")
dep_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_dep))
```


### Overall Satisfaction

```{r QSTIS_plot_overall}
dep_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r QSTIS_plot_gender}
dep_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_dep)
```



### Satisfaction by Race

```{r QSTIS_plot_race}
dep_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_dep)
```


