# Course Satisfaction


## CAS CH131 Course Satisfaction


```{r CASCH131_input}
input <- list(selected_course = "CAS CH131")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASCH131_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASCH131_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASCH131_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS CS 111 Course Satisfaction


```{r CASCS111_input}
input <- list(selected_course = "CAS CS 111")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASCS111_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASCS111_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASCS111_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS CS112 Course Satisfaction


```{r CASCS112_input}
input <- list(selected_course = "CAS CS112")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASCS112_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASCS112_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASCS112_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS CS131 Course Satisfaction


```{r CASCS131_input}
input <- list(selected_course = "CAS CS131")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASCS131_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASCS131_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASCS131_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS CS132 Course Satisfaction


```{r CASCS132_input}
input <- list(selected_course = "CAS CS132")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASCS132_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASCS132_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASCS132_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS CS210 Course Satisfaction


```{r CASCS210_input}
input <- list(selected_course = "CAS CS210")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASCS210_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASCS210_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASCS210_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS CS235 Course Satisfaction


```{r CASCS235_input}
input <- list(selected_course = "CAS CS235")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASCS235_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASCS235_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASCS235_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS CS237 Course Satisfaction


```{r CASCS237_input}
input <- list(selected_course = "CAS CS237")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASCS237_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASCS237_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASCS237_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS CS320 Course Satisfaction


```{r CASCS320_input}
input <- list(selected_course = "CAS CS320")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASCS320_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASCS320_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASCS320_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS CS330 Course Satisfaction


```{r CASCS330_input}
input <- list(selected_course = "CAS CS330")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASCS330_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASCS330_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASCS330_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS CS332 Course Satisfaction


```{r CASCS332_input}
input <- list(selected_course = "CAS CS332")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASCS332_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASCS332_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASCS332_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS CS350 Course Satisfaction


```{r CASCS350_input}
input <- list(selected_course = "CAS CS350")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASCS350_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASCS350_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASCS350_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS MA 113 Course Satisfaction


```{r CASMA113_input}
input <- list(selected_course = "CAS MA 113")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASMA113_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASMA113_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASMA113_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS MA 115 Course Satisfaction


```{r CASMA115_input}
input <- list(selected_course = "CAS MA 115")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASMA115_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASMA115_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASMA115_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS MA 116 Course Satisfaction


```{r CASMA116_input}
input <- list(selected_course = "CAS MA 116")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASMA116_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASMA116_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASMA116_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS MA 121 Course Satisfaction


```{r CASMA121_input}
input <- list(selected_course = "CAS MA 121")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASMA121_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASMA121_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASMA121_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS MA 122 Course Satisfaction


```{r CASMA122_input}
input <- list(selected_course = "CAS MA 122")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASMA122_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASMA122_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASMA122_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS MA 123 Course Satisfaction


```{r CASMA123_input}
input <- list(selected_course = "CAS MA 123")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASMA123_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASMA123_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASMA123_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS MA 124 Course Satisfaction


```{r CASMA124_input}
input <- list(selected_course = "CAS MA 124")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASMA124_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASMA124_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASMA124_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS MA 127 Course Satisfaction


```{r CASMA127_input}
input <- list(selected_course = "CAS MA 127")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASMA127_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASMA127_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASMA127_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS MA 129 Course Satisfaction


```{r CASMA129_input}
input <- list(selected_course = "CAS MA 129")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASMA129_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASMA129_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASMA129_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS MA 142 Course Satisfaction


```{r CASMA142_input}
input <- list(selected_course = "CAS MA 142")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASMA142_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASMA142_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASMA142_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS MA 193 Course Satisfaction


```{r CASMA193_input}
input <- list(selected_course = "CAS MA 193")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASMA193_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASMA193_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASMA193_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS MA 213 Course Satisfaction


```{r CASMA213_input}
input <- list(selected_course = "CAS MA 213")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASMA213_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASMA213_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASMA213_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS MA 214 Course Satisfaction


```{r CASMA214_input}
input <- list(selected_course = "CAS MA 214")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASMA214_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASMA214_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASMA214_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS MA 225 Course Satisfaction


```{r CASMA225_input}
input <- list(selected_course = "CAS MA 225")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASMA225_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASMA225_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASMA225_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS MA 226 Course Satisfaction


```{r CASMA226_input}
input <- list(selected_course = "CAS MA 226")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASMA226_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASMA226_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASMA226_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS MA 230 Course Satisfaction


```{r CASMA230_input}
input <- list(selected_course = "CAS MA 230")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASMA230_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASMA230_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASMA230_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS MA 231 Course Satisfaction


```{r CASMA231_input}
input <- list(selected_course = "CAS MA 231")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASMA231_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASMA231_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASMA231_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS MA 242 Course Satisfaction


```{r CASMA242_input}
input <- list(selected_course = "CAS MA 242")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASMA242_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASMA242_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASMA242_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS MA 293 Course Satisfaction


```{r CASMA293_input}
input <- list(selected_course = "CAS MA 293")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASMA293_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASMA293_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASMA293_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS MA 294 Course Satisfaction


```{r CASMA294_input}
input <- list(selected_course = "CAS MA 294")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASMA294_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASMA294_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASMA294_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS MA 442 Course Satisfaction


```{r CASMA442_input}
input <- list(selected_course = "CAS MA 442")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASMA442_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASMA442_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASMA442_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS MA 614 Course Satisfaction


```{r CASMA614_input}
input <- list(selected_course = "CAS MA 614")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASMA614_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASMA614_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASMA614_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS PY211 Course Satisfaction


```{r CASPY211_input}
input <- list(selected_course = "CAS PY211")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASPY211_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASPY211_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASPY211_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CAS PY212 Course Satisfaction


```{r CASPY212_input}
input <- list(selected_course = "CAS PY212")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CASPY212_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CASPY212_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CASPY212_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CDS DS 110 Course Satisfaction


```{r CDSDS110_input}
input <- list(selected_course = "CDS DS 110")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CDSDS110_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CDSDS110_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CDSDS110_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CDS DS 120 Course Satisfaction


```{r CDSDS120_input}
input <- list(selected_course = "CDS DS 120")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CDSDS120_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CDSDS120_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CDSDS120_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CDS DS 121 Course Satisfaction


```{r CDSDS121_input}
input <- list(selected_course = "CDS DS 121")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CDSDS121_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CDSDS121_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CDSDS121_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CDS DS 122 Course Satisfaction


```{r CDSDS122_input}
input <- list(selected_course = "CDS DS 122")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CDSDS122_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CDSDS122_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CDSDS122_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CDS DS 210 Course Satisfaction


```{r CDSDS210_input}
input <- list(selected_course = "CDS DS 210")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CDSDS210_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CDSDS210_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CDSDS210_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CDS DS 310 Course Satisfaction


```{r CDSDS310_input}
input <- list(selected_course = "CDS DS 310")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CDSDS310_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CDSDS310_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CDSDS310_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CDS DS 320 Course Satisfaction


```{r CDSDS320_input}
input <- list(selected_course = "CDS DS 320")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CDSDS320_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CDSDS320_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CDSDS320_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CDS DS 340 Course Satisfaction


```{r CDSDS340_input}
input <- list(selected_course = "CDS DS 340")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CDSDS340_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CDSDS340_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CDSDS340_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CDS DS 380 Course Satisfaction


```{r CDSDS380_input}
input <- list(selected_course = "CDS DS 380")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CDSDS380_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CDSDS380_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CDSDS380_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## CDS DS 457 Course Satisfaction


```{r CDSDS457_input}
input <- list(selected_course = "CDS DS 457")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r CDSDS457_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r CDSDS457_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r CDSDS457_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## ENG EC327 Course Satisfaction


```{r ENGEC327_input}
input <- list(selected_course = "ENG EC327")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r ENGEC327_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r ENGEC327_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r ENGEC327_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## ENG EC330 Course Satisfaction


```{r ENGEC330_input}
input <- list(selected_course = "ENG EC330")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r ENGEC330_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r ENGEC330_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r ENGEC330_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## ENG EK100 Course Satisfaction


```{r ENGEK100_input}
input <- list(selected_course = "ENG EK100")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r ENGEK100_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r ENGEK100_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r ENGEK100_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## ENG EK103 Course Satisfaction


```{r ENGEK103_input}
input <- list(selected_course = "ENG EK103")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r ENGEK103_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r ENGEK103_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r ENGEK103_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## ENG EK125 Course Satisfaction


```{r ENGEK125_input}
input <- list(selected_course = "ENG EK125")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r ENGEK125_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r ENGEK125_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r ENGEK125_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## ENG EK131 Course Satisfaction


```{r ENGEK131_input}
input <- list(selected_course = "ENG EK131")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r ENGEK131_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r ENGEK131_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r ENGEK131_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## ENG EK210 Course Satisfaction


```{r ENGEK210_input}
input <- list(selected_course = "ENG EK210")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r ENGEK210_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r ENGEK210_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r ENGEK210_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## ENG EK301 Course Satisfaction


```{r ENGEK301_input}
input <- list(selected_course = "ENG EK301")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r ENGEK301_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r ENGEK301_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r ENGEK301_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## ENG EK307 Course Satisfaction


```{r ENGEK307_input}
input <- list(selected_course = "ENG EK307")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r ENGEK307_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r ENGEK307_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r ENGEK307_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## QST BA 476 Course Satisfaction


```{r QSTBA476_input}
input <- list(selected_course = "QST BA 476")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r QSTBA476_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r QSTBA476_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r QSTBA476_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## QST IS 223 Course Satisfaction


```{r QSTIS223_input}
input <- list(selected_course = "QST IS 223")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r QSTIS223_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r QSTIS223_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r QSTIS223_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## QST IS 428 Course Satisfaction


```{r QSTIS428_input}
input <- list(selected_course = "QST IS 428")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r QSTIS428_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r QSTIS428_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r QSTIS428_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## QST IS 454 Course Satisfaction


```{r QSTIS454_input}
input <- list(selected_course = "QST IS 454")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r QSTIS454_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r QSTIS454_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r QSTIS454_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## QST IS 465 Course Satisfaction


```{r QSTIS465_input}
input <- list(selected_course = "QST IS 465")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r QSTIS465_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r QSTIS465_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r QSTIS465_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## QST IS 467 Course Satisfaction


```{r QSTIS467_input}
input <- list(selected_course = "QST IS 467")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r QSTIS467_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r QSTIS467_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r QSTIS467_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## QST IS 469 Course Satisfaction


```{r QSTIS469_input}
input <- list(selected_course = "QST IS 469")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r QSTIS469_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r QSTIS469_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r QSTIS469_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## QST IS 474 Course Satisfaction


```{r QSTIS474_input}
input <- list(selected_course = "QST IS 474")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r QSTIS474_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r QSTIS474_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r QSTIS474_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```



## QST IS 479 Course Satisfaction


```{r QSTIS479_input}
input <- list(selected_course = "QST IS 479")
course_select_df <-
  course_ldf %>%
    filter(str_detect(question_text, input$selected_course))
any_response <- nrow(course_select_df) > 0
```


### Overall Satisfaction

```{r QSTIS479_plot_overall, eval=any_response}
course_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Satisfaction by Gender

```{r QSTIS479_plot_gender, eval=any_response}
course_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_course)
```



### Satisfaction by Race

```{r QSTIS479_plot_race, eval=any_response}
course_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_course)
```

