# Agreement Statements



## How much do you agree with the statement "Diversity in my major is important."?


```{r Diversity_in_my_major_is_important__input}
input <- list(selected_agr_q = "Diversity in my major is important.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r Diversity_in_my_major_is_important__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r Diversity_in_my_major_is_important__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r Diversity_in_my_major_is_important__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "I am comfortable going to my advisors for my major."?


```{r I_am_comfortable_going_to_my_advisors_for_my_major__input}
input <- list(selected_agr_q = "I am comfortable going to my advisors for my major.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r I_am_comfortable_going_to_my_advisors_for_my_major__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r I_am_comfortable_going_to_my_advisors_for_my_major__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r I_am_comfortable_going_to_my_advisors_for_my_major__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "I am comfortable talking about my background and cultural experiences."?


```{r I_am_comfortable_talking_about_my_background_and_cultural_experiences__input}
input <- list(selected_agr_q = "I am comfortable talking about my background and cultural experiences.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r I_am_comfortable_talking_about_my_background_and_cultural_experiences__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r I_am_comfortable_talking_about_my_background_and_cultural_experiences__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r I_am_comfortable_talking_about_my_background_and_cultural_experiences__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "I am insulted because of my abilities/disabilities"?


```{r I_am_insulted_because_of_my_abilities_disabilities_input}
input <- list(selected_agr_q = "I am insulted because of my abilities/disabilities")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r I_am_insulted_because_of_my_abilities_disabilities_plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r I_am_insulted_because_of_my_abilities_disabilities_plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r I_am_insulted_because_of_my_abilities_disabilities_plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "I am insulted because of my gender identity."?


```{r I_am_insulted_because_of_my_gender_identity__input}
input <- list(selected_agr_q = "I am insulted because of my gender identity.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r I_am_insulted_because_of_my_gender_identity__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r I_am_insulted_because_of_my_gender_identity__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r I_am_insulted_because_of_my_gender_identity__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "I am insulted because of my race or ethnicity."?


```{r I_am_insulted_because_of_my_race_or_ethnicity__input}
input <- list(selected_agr_q = "I am insulted because of my race or ethnicity.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r I_am_insulted_because_of_my_race_or_ethnicity__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r I_am_insulted_because_of_my_race_or_ethnicity__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r I_am_insulted_because_of_my_race_or_ethnicity__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "I am insulted because of my religion"?


```{r I_am_insulted_because_of_my_religion_input}
input <- list(selected_agr_q = "I am insulted because of my religion")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r I_am_insulted_because_of_my_religion_plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r I_am_insulted_because_of_my_religion_plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r I_am_insulted_because_of_my_religion_plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "I am overlooked or ignored when working in a group."?


```{r I_am_overlooked_or_ignored_when_working_in_a_group__input}
input <- list(selected_agr_q = "I am overlooked or ignored when working in a group.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r I_am_overlooked_or_ignored_when_working_in_a_group__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r I_am_overlooked_or_ignored_when_working_in_a_group__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r I_am_overlooked_or_ignored_when_working_in_a_group__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "I am satisfied with my personal experience regarding diversity and inclusion in my major's department."?


```{r I_am_satisfied_with_my_personal_experience_regarding_diversity_and_inclusion_in_my_major_s_department__input}
input <- list(selected_agr_q = "I am satisfied with my personal experience regarding diversity and inclusion in my major's department.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r I_am_satisfied_with_my_personal_experience_regarding_diversity_and_inclusion_in_my_major_s_department__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r I_am_satisfied_with_my_personal_experience_regarding_diversity_and_inclusion_in_my_major_s_department__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r I_am_satisfied_with_my_personal_experience_regarding_diversity_and_inclusion_in_my_major_s_department__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "I am satisfied with the social climate at my major's department"?


```{r I_am_satisfied_with_the_social_climate_at_my_major_s_department_input}
input <- list(selected_agr_q = "I am satisfied with the social climate at my major's department")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r I_am_satisfied_with_the_social_climate_at_my_major_s_department_plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r I_am_satisfied_with_the_social_climate_at_my_major_s_department_plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r I_am_satisfied_with_the_social_climate_at_my_major_s_department_plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "I am stressed."?


```{r I_am_stressed__input}
input <- list(selected_agr_q = "I am stressed.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r I_am_stressed__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r I_am_stressed__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r I_am_stressed__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "I am treated fairly and equitably by faculty in my major."?


```{r I_am_treated_fairly_and_equitably_by_faculty_in_my_major__input}
input <- list(selected_agr_q = "I am treated fairly and equitably by faculty in my major.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r I_am_treated_fairly_and_equitably_by_faculty_in_my_major__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r I_am_treated_fairly_and_equitably_by_faculty_in_my_major__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r I_am_treated_fairly_and_equitably_by_faculty_in_my_major__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "I am treated fairly and equitably by my peers in my major."?


```{r I_am_treated_fairly_and_equitably_by_my_peers_in_my_major__input}
input <- list(selected_agr_q = "I am treated fairly and equitably by my peers in my major.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r I_am_treated_fairly_and_equitably_by_my_peers_in_my_major__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r I_am_treated_fairly_and_equitably_by_my_peers_in_my_major__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r I_am_treated_fairly_and_equitably_by_my_peers_in_my_major__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "I am treated fairly and equitably by staff in my major."?


```{r I_am_treated_fairly_and_equitably_by_staff_in_my_major__input}
input <- list(selected_agr_q = "I am treated fairly and equitably by staff in my major.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r I_am_treated_fairly_and_equitably_by_staff_in_my_major__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r I_am_treated_fairly_and_equitably_by_staff_in_my_major__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r I_am_treated_fairly_and_equitably_by_staff_in_my_major__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "I feel like an outsider."?


```{r I_feel_like_an_outsider__input}
input <- list(selected_agr_q = "I feel like an outsider.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r I_feel_like_an_outsider__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r I_feel_like_an_outsider__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r I_feel_like_an_outsider__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "I feel like I'll be judged by my peers if I make a mistake."?


```{r I_feel_like_I_ll_be_judged_by_my_peers_if_I_make_a_mistake__input}
input <- list(selected_agr_q = "I feel like I'll be judged by my peers if I make a mistake.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r I_feel_like_I_ll_be_judged_by_my_peers_if_I_make_a_mistake__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r I_feel_like_I_ll_be_judged_by_my_peers_if_I_make_a_mistake__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r I_feel_like_I_ll_be_judged_by_my_peers_if_I_make_a_mistake__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "I feel stressed."?


```{r I_feel_stressed__input}
input <- list(selected_agr_q = "I feel stressed.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r I_feel_stressed__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r I_feel_stressed__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r I_feel_stressed__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "I feel supported by my peers."?


```{r I_feel_supported_by_my_peers__input}
input <- list(selected_agr_q = "I feel supported by my peers.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r I_feel_supported_by_my_peers__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r I_feel_supported_by_my_peers__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r I_feel_supported_by_my_peers__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "I find it difficult to juggle all of my responsibilities."?


```{r I_find_it_difficult_to_juggle_all_of_my_responsibilities__input}
input <- list(selected_agr_q = "I find it difficult to juggle all of my responsibilities.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r I_find_it_difficult_to_juggle_all_of_my_responsibilities__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r I_find_it_difficult_to_juggle_all_of_my_responsibilities__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r I_find_it_difficult_to_juggle_all_of_my_responsibilities__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "I had an easy transition from high school to college."?


```{r I_had_an_easy_transition_from_high_school_to_college__input}
input <- list(selected_agr_q = "I had an easy transition from high school to college.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r I_had_an_easy_transition_from_high_school_to_college__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r I_had_an_easy_transition_from_high_school_to_college__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r I_had_an_easy_transition_from_high_school_to_college__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "I have a solid support system."?


```{r I_have_a_solid_support_system__input}
input <- list(selected_agr_q = "I have a solid support system.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r I_have_a_solid_support_system__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r I_have_a_solid_support_system__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r I_have_a_solid_support_system__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "I have to work harder than others to be valued equally within my major."?


```{r I_have_to_work_harder_than_others_to_be_valued_equally_within_my_major__input}
input <- list(selected_agr_q = "I have to work harder than others to be valued equally within my major.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r I_have_to_work_harder_than_others_to_be_valued_equally_within_my_major__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r I_have_to_work_harder_than_others_to_be_valued_equally_within_my_major__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r I_have_to_work_harder_than_others_to_be_valued_equally_within_my_major__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "I made the right choice by attending BU."?


```{r I_made_the_right_choice_by_attending_BU__input}
input <- list(selected_agr_q = "I made the right choice by attending BU.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r I_made_the_right_choice_by_attending_BU__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r I_made_the_right_choice_by_attending_BU__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r I_made_the_right_choice_by_attending_BU__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "My advisors for my major are helpful."?


```{r My_advisors_for_my_major_are_helpful__input}
input <- list(selected_agr_q = "My advisors for my major are helpful.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r My_advisors_for_my_major_are_helpful__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r My_advisors_for_my_major_are_helpful__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r My_advisors_for_my_major_are_helpful__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "My friend group is gender-diverse."?


```{r My_friend_group_is_gender_diverse__input}
input <- list(selected_agr_q = "My friend group is gender-diverse.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r My_friend_group_is_gender_diverse__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r My_friend_group_is_gender_diverse__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r My_friend_group_is_gender_diverse__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "My friend group is racially diverse."?


```{r My_friend_group_is_racially_diverse__input}
input <- list(selected_agr_q = "My friend group is racially diverse.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r My_friend_group_is_racially_diverse__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r My_friend_group_is_racially_diverse__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r My_friend_group_is_racially_diverse__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "My peers are respectful of people of different affiliations/political views"?


```{r My_peers_are_respectful_of_people_of_different_affiliations_political_views_input}
input <- list(selected_agr_q = "My peers are respectful of people of different affiliations/political views")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r My_peers_are_respectful_of_people_of_different_affiliations_political_views_plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r My_peers_are_respectful_of_people_of_different_affiliations_political_views_plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r My_peers_are_respectful_of_people_of_different_affiliations_political_views_plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "My peers are respectful of people of different genders."?


```{r My_peers_are_respectful_of_people_of_different_genders__input}
input <- list(selected_agr_q = "My peers are respectful of people of different genders.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r My_peers_are_respectful_of_people_of_different_genders__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r My_peers_are_respectful_of_people_of_different_genders__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r My_peers_are_respectful_of_people_of_different_genders__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "My peers are respectful of people of different races."?


```{r My_peers_are_respectful_of_people_of_different_races__input}
input <- list(selected_agr_q = "My peers are respectful of people of different races.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r My_peers_are_respectful_of_people_of_different_races__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r My_peers_are_respectful_of_people_of_different_races__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r My_peers_are_respectful_of_people_of_different_races__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "My peers are respectful of people of different religions."?


```{r My_peers_are_respectful_of_people_of_different_religions__input}
input <- list(selected_agr_q = "My peers are respectful of people of different religions.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r My_peers_are_respectful_of_people_of_different_religions__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r My_peers_are_respectful_of_people_of_different_religions__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r My_peers_are_respectful_of_people_of_different_religions__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "Professors are respectful of people of different affiliations/political views"?


```{r Professors_are_respectful_of_people_of_different_affiliations_political_views_input}
input <- list(selected_agr_q = "Professors are respectful of people of different affiliations/political views")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r Professors_are_respectful_of_people_of_different_affiliations_political_views_plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r Professors_are_respectful_of_people_of_different_affiliations_political_views_plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r Professors_are_respectful_of_people_of_different_affiliations_political_views_plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "Professors are respectful of people of different genders."?


```{r Professors_are_respectful_of_people_of_different_genders__input}
input <- list(selected_agr_q = "Professors are respectful of people of different genders.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r Professors_are_respectful_of_people_of_different_genders__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r Professors_are_respectful_of_people_of_different_genders__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r Professors_are_respectful_of_people_of_different_genders__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "Professors are respectful of people of different races."?


```{r Professors_are_respectful_of_people_of_different_races__input}
input <- list(selected_agr_q = "Professors are respectful of people of different races.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r Professors_are_respectful_of_people_of_different_races__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r Professors_are_respectful_of_people_of_different_races__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r Professors_are_respectful_of_people_of_different_races__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "Professors are respectful of people of different religions."?


```{r Professors_are_respectful_of_people_of_different_religions__input}
input <- list(selected_agr_q = "Professors are respectful of people of different religions.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r Professors_are_respectful_of_people_of_different_religions__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r Professors_are_respectful_of_people_of_different_religions__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r Professors_are_respectful_of_people_of_different_religions__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "Professors are willing to help me with assignments."?


```{r Professors_are_willing_to_help_me_with_assignments__input}
input <- list(selected_agr_q = "Professors are willing to help me with assignments.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r Professors_are_willing_to_help_me_with_assignments__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r Professors_are_willing_to_help_me_with_assignments__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r Professors_are_willing_to_help_me_with_assignments__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "Professors call on me in class."?


```{r Professors_call_on_me_in_class__input}
input <- list(selected_agr_q = "Professors call on me in class.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r Professors_call_on_me_in_class__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r Professors_call_on_me_in_class__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r Professors_call_on_me_in_class__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "Professors care about me."?


```{r Professors_care_about_me__input}
input <- list(selected_agr_q = "Professors care about me.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r Professors_care_about_me__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r Professors_care_about_me__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r Professors_care_about_me__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## How much do you agree with the statement "When I speak up, I feel like my opinion matters."?


```{r When_I_speak_up_I_feel_like_my_opinion_matters__input}
input <- list(selected_agr_q = "When I speak up, I feel like my opinion matters.")
agr_select_df <-
  agreement_ldf %>%
    filter(str_detect(question_text, input$selected_agr_q))
```


### Overall Agreement

```{r When_I_speak_up_I_feel_like_my_opinion_matters__plot_overall}
agr_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r When_I_speak_up_I_feel_like_my_opinion_matters__plot_gender}
agr_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r When_I_speak_up_I_feel_like_my_opinion_matters__plot_race}
agr_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```

