# Adjective Range Questions



## Please select one option between each set of adjectives "Ageist:Non-ageist"


```{r Ageist_Non_ageist_input}
input <- list(selected_adj_q = "Ageist:Non-ageist")
adj_select_df <-
  adj_ldf %>%
    filter(str_detect(question_text, input$selected_adj_q))
```


### Overall Agreement

```{r Ageist_Non_ageist_plot_overall}
adj_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r Ageist_Non_ageist_plot_gender}
adj_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r Ageist_Non_ageist_plot_race}
adj_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## Please select one option between each set of adjectives "Competitive:Cooperative"


```{r Competitive_Cooperative_input}
input <- list(selected_adj_q = "Competitive:Cooperative")
adj_select_df <-
  adj_ldf %>%
    filter(str_detect(question_text, input$selected_adj_q))
```


### Overall Agreement

```{r Competitive_Cooperative_plot_overall}
adj_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r Competitive_Cooperative_plot_gender}
adj_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r Competitive_Cooperative_plot_race}
adj_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## Please select one option between each set of adjectives "Contentious:Collegial"


```{r Contentious_Collegial_input}
input <- list(selected_adj_q = "Contentious:Collegial")
adj_select_df <-
  adj_ldf %>%
    filter(str_detect(question_text, input$selected_adj_q))
```


### Overall Agreement

```{r Contentious_Collegial_plot_overall}
adj_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r Contentious_Collegial_plot_gender}
adj_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r Contentious_Collegial_plot_race}
adj_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## Please select one option between each set of adjectives "Disrespectful:Respectful"


```{r Disrespectful_Respectful_input}
input <- list(selected_adj_q = "Disrespectful:Respectful")
adj_select_df <-
  adj_ldf %>%
    filter(str_detect(question_text, input$selected_adj_q))
```


### Overall Agreement

```{r Disrespectful_Respectful_plot_overall}
adj_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r Disrespectful_Respectful_plot_gender}
adj_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r Disrespectful_Respectful_plot_race}
adj_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## Please select one option between each set of adjectives "Elitist:Non-elitist"


```{r Elitist_Non_elitist_input}
input <- list(selected_adj_q = "Elitist:Non-elitist")
adj_select_df <-
  adj_ldf %>%
    filter(str_detect(question_text, input$selected_adj_q))
```


### Overall Agreement

```{r Elitist_Non_elitist_plot_overall}
adj_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r Elitist_Non_elitist_plot_gender}
adj_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r Elitist_Non_elitist_plot_race}
adj_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## Please select one option between each set of adjectives "Homogenous:Diverse"


```{r Homogenous_Diverse_input}
input <- list(selected_adj_q = "Homogenous:Diverse")
adj_select_df <-
  adj_ldf %>%
    filter(str_detect(question_text, input$selected_adj_q))
```


### Overall Agreement

```{r Homogenous_Diverse_plot_overall}
adj_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r Homogenous_Diverse_plot_gender}
adj_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r Homogenous_Diverse_plot_race}
adj_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## Please select one option between each set of adjectives "Homophobic:Non-homophobic"


```{r Homophobic_Non_homophobic_input}
input <- list(selected_adj_q = "Homophobic:Non-homophobic")
adj_select_df <-
  adj_ldf %>%
    filter(str_detect(question_text, input$selected_adj_q))
```


### Overall Agreement

```{r Homophobic_Non_homophobic_plot_overall}
adj_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r Homophobic_Non_homophobic_plot_gender}
adj_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r Homophobic_Non_homophobic_plot_race}
adj_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## Please select one option between each set of adjectives "Hostile:Friendly"


```{r Hostile_Friendly_input}
input <- list(selected_adj_q = "Hostile:Friendly")
adj_select_df <-
  adj_ldf %>%
    filter(str_detect(question_text, input$selected_adj_q))
```


### Overall Agreement

```{r Hostile_Friendly_plot_overall}
adj_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r Hostile_Friendly_plot_gender}
adj_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r Hostile_Friendly_plot_race}
adj_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## Please select one option between each set of adjectives "Individualistic:Collaborative"


```{r Individualistic_Collaborative_input}
input <- list(selected_adj_q = "Individualistic:Collaborative")
adj_select_df <-
  adj_ldf %>%
    filter(str_detect(question_text, input$selected_adj_q))
```


### Overall Agreement

```{r Individualistic_Collaborative_plot_overall}
adj_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r Individualistic_Collaborative_plot_gender}
adj_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r Individualistic_Collaborative_plot_race}
adj_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## Please select one option between each set of adjectives "Racist:Non-racist"


```{r Racist_Non_racist_input}
input <- list(selected_adj_q = "Racist:Non-racist")
adj_select_df <-
  adj_ldf %>%
    filter(str_detect(question_text, input$selected_adj_q))
```


### Overall Agreement

```{r Racist_Non_racist_plot_overall}
adj_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r Racist_Non_racist_plot_gender}
adj_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r Racist_Non_racist_plot_race}
adj_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## Please select one option between each set of adjectives "Sexist:Non-sexist"


```{r Sexist_Non_sexist_input}
input <- list(selected_adj_q = "Sexist:Non-sexist")
adj_select_df <-
  adj_ldf %>%
    filter(str_detect(question_text, input$selected_adj_q))
```


### Overall Agreement

```{r Sexist_Non_sexist_plot_overall}
adj_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r Sexist_Non_sexist_plot_gender}
adj_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r Sexist_Non_sexist_plot_race}
adj_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## Please select one option between each set of adjectives "Unsupportive:Supportive"


```{r Unsupportive_Supportive_input}
input <- list(selected_adj_q = "Unsupportive:Supportive")
adj_select_df <-
  adj_ldf %>%
    filter(str_detect(question_text, input$selected_adj_q))
```


### Overall Agreement

```{r Unsupportive_Supportive_plot_overall}
adj_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r Unsupportive_Supportive_plot_gender}
adj_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r Unsupportive_Supportive_plot_race}
adj_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



## Please select one option between each set of adjectives "Unwelcoming:Welcoming"


```{r Unwelcoming_Welcoming_input}
input <- list(selected_adj_q = "Unwelcoming:Welcoming")
adj_select_df <-
  adj_ldf %>%
    filter(str_detect(question_text, input$selected_adj_q))
```


### Overall Agreement

```{r Unwelcoming_Welcoming_plot_overall}
adj_select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))
```

### Agreement by Gender

```{r Unwelcoming_Welcoming_plot_gender}
adj_select_df %>%
  group_by(gender) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```



### Agreement by Race

```{r Unwelcoming_Welcoming_plot_race}
adj_select_df %>%
  simplify_race_var() %>%
  group_by(race) %>%
  count(response, name = "count", .drop = FALSE) %>%
  mutate(prop = count / sum(count)) %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)
```

