---
title: "DEI Second Tables"
author: "Anna Yaggi"
date: '2022-09-28'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(readxl)
dei_clean_data <- read_excel("~/Desktop/Spark!/DEI Project/dei_clean_data.xlsx")
attach(dei_clean_data)
```


Major breakdown table
```{r}
major = table(dei_clean_data$Q1)
major_table = as.data.frame(major)
names(major_table)[1] = "Major"
major_table
```

Grad year breakdown table
```{r}
gradyear = table(dei_clean_data$Q2)
gradyear_table = as.data.frame(gradyear)
names(gradyear_table)[1] = "Graduation Year"
gradyear_table
```

First Generation breakdown table
```{r}
firstgen = table(dei_clean_data$Q4)
firstgen_table = as.data.frame(firstgen)
names(firstgen_table)[1] = "First generation student?"
firstgen_table
```

International student breakdown table
```{r}
inter = table(dei_clean_data$Q5)
inter_table = as.data.frame(inter)
names(inter_table)[1] = "International  student?"
inter_table
```

Gender Identity Breakdown table
```{r}
genderI = table(dei_clean_data$Q6)
genderI_table = as.data.frame(genderI)
names(genderI_table)[1] = "Gender Identity"
genderI_table
```

Race/Ethnicity breakdown table
```{r}
race = table(dei_clean_data$Q7)
race_table = as.data.frame(race)
names(race_table)[1] =  "selected race(s)/ ethnicity"
race_table
```

Involved in Professional / academic orgs breakdown table***problem!!
```{r}
profaca = table(dei_clean_data$Q19)
profaca_table = as.data.frame(profaca)
names(profaca_table)[1] = "Involved in professional/academic organizations?"
```

Involved in other orgs breakdowntable***problem!!
```{r}
otherorg = table(dei_clean_data$Q20)
otherorg_table = as.data.frame(otherorg)
names(otherorg_table)[1] = "Involved in other organizations?"
```

Job breakdown table
```{r}
job = table(dei_clean_data$Q21)
job_table = as.data.frame(job)
names(job_table)[1] = "job?"
job_table
```

Financial aid / Schol. Requirements table
```{r}
finaid = table(dei_clean_data$Q22)
finaid_table = as.data.frame(finaid)
names(finaid_table)[1] = "financial aid/ scholarship requirments?"
finaid_table
```




Satisfaction with CS111 table
```{r}
CS111 = table(dei_clean_data$Q11_1)
CS111_table =  as.data.frame(CS111)
names(CS111_table)[1] = "Satsifaction with  CS111"
CS111_table
```



International Student(Y), Financial Aid (X)
```{r}
library(ggplot2)
ggplot(data  = dei_clean_data)+
  geom_point(mapping = aes(x=stringr::str_wrap(Q22,15),stringr::str_wrap(Q5,15)), position = "jitter")

```


CS111 Satisfaction(X) and gender identity (Y)
```{r}
library(ggplot2)
ggplot(data  = dei_clean_data)+
  geom_point(mapping = aes(x=stringr::str_wrap(Q11_1,10),stringr::str_wrap(Q6,15)), position = "jitter")
```

```{r}
library(ggplot2)
ggplot(data  = dei_clean_data)+
  geom_bar(mapping = aes(x=stringr::str_wrap(Q11_1,10), fill = Q11_1))
```





