
## {{{title}}} {.tabset .tabset-fade .tabset-pills}

```{r {{{selected_q_code}}}_input}
input <- list(selected_q = "{{{selected_q}}}")
select_df <-
  {{{which_df}}}_ldf %>%
    filter(str_detect(question_text, input$selected_q))
any_response <- nrow(select_df) > 0
```

### {{{subsection_title}}} Overall

```{r {{{selected_q_code}}}_plot_overall, eval=any_response}
select_df %>%
  ggplot(aes(x = response)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(n.dodge = 2), drop = FALSE)

select_df %>%
  count_prop_complete() %>%
  rename(number = count, percent = prop) %>% 
  gt::gt() %>% 
  fmt_percent(percent, decimals = 1)

ex <- select_df %>% 
  summarize(nr = sum(response == response[1]), response = response[1], n = n())
nt <- ex$n
```

This represents a total of `r ex$n` responses. Of these `r ex$nr` responses were `r ex$response`, representing `r scales::percent(ex$nr/ex$n)` of the total.

### {{{subsection_title}}} by Gender

```{r {{{selected_q_code}}}_plot_gender, eval=any_response}
gdf <- select_df %>%
  count_prop_complete(gender)

gdf %>%
  ggplot(aes(x = response, fill = gender)) %>%
  stack_freq_prop(title = input$selected_agr_q)

gdf %>% 
  transmute(
    gender,
    response,
    value = str_glue("{count} ({scales::percent(prop)})")
  ) %>% 
  pivot_wider(names_from = "response", values_from = "value") %>% 
  ungroup() %>% 
  gt::gt(rowname_col = "race") %>% 
  sub_missing()

ex <- gdf %>% mutate(n = sum(count)) %>% ungroup() %>% filter(row_number() == 1)

```

Out of the `r nt` total respondents, `r ex$n` (`r scales::percent(ex$n / nt)`) indicated `r ex$gender` as their gender.
Of these `r ex$n`, `r ex$count` (`r scales::percent(ex$prop)`) responded  with `r ex$response`.

### {{{subsection_title}}} by Race

```{r {{{selected_q_code}}}_plot_race, eval=any_response}
rdf <- select_df %>%
  count_prop_complete(race)

rdf %>%
  ggplot(aes(x = response, fill = race)) %>%
  stack_freq_prop(title = input$selected_agr_q)


rdf %>% 
  transmute(
    race,
    response,
    value = str_glue("{count}\n\n({scales::percent(prop)})")
  ) %>% 
  pivot_wider(names_from = "response", values_from = "value") %>% 
  ungroup() %>% 
  gt::gt(rowname_col = "race") %>% 
  sub_missing()
ex <- rdf %>% mutate(n = sum(count)) %>% ungroup() %>% filter(row_number() == 1)

```

Out of the `r nt` total respondents, `r ex$n` (`r scales::percent(ex$n / nt)`) indicated `r ex$race` as their race.
Of these `r ex$n`, `r ex$count` (`r scales::percent(ex$prop)`) responded  with `r ex$response`.



### {{{subsection_title}}} by International status

```{r {{{selected_q_code}}}_plot_international, eval=any_response}
idf <- select_df %>%
  count_prop_complete(international)

idf %>%
  ggplot(aes(x = response, fill = international)) %>%
  stack_freq_prop(title = input$selected_agr_q)


idf %>%
  transmute(
    international,
    response,
    value = str_glue("{count}\n\n({scales::percent(prop)})")
  ) %>% 
  pivot_wider(names_from = "response", values_from = "value") %>% 
  ungroup() %>% 
  gt::gt(rowname_col = "international") %>% 
  sub_missing()
ex <- idf %>% mutate(n = sum(count)) %>% ungroup() %>% filter(row_number() == 1)

```

Out of the `r nt` total respondents, `r ex$n` (`r scales::percent(ex$n / nt)`) answered "`r ex$international`" to the question "Are you an international student?".
Of these `r ex$n`, `r ex$count` (`r scales::percent(ex$prop)`) responded  with `r ex$response`.



### {{{subsection_title}}} by First-gen college status

```{r {{{selected_q_code}}}_plot_first_gen, eval=any_response}
fdf <- select_df %>%
  count_prop_complete(first_gen)
fdf %>%
  ggplot(aes(x = response, fill = first_gen)) %>%
  stack_freq_prop(title = input$selected_agr_q)


fdf %>% 
  transmute(
    first_gen,
    response,
    value = str_glue("{count}\n\n({scales::percent(prop)})")
  ) %>% 
  pivot_wider(names_from = "response", values_from = "value") %>% 
  ungroup() %>% 
  gt::gt(rowname_col = "first_gen") %>% 
  sub_missing()
ex <- fdf %>% mutate(n = sum(count)) %>% ungroup() %>% filter(row_number() == 1)

```

Out of the `r nt` total respondents, `r ex$n` (`r scales::percent(ex$n / nt)`) answered "`r ex$first_gen`" to the question "Are you a first generation college student?".
Of these `r ex$n`, `r ex$count` (`r scales::percent(ex$prop)`) responded  with `r ex$response`.
